---
title: "DC WhatsApp Assignment"
author: "Surendra Dattatrey"
Location: "Delhi NCR"
date: "19 March 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
We gathered lots of whats app Data for almost 1.5 weeks. and try to get some information about travel stories,  which was unknown to me till now.

```{r cars}
rm(list = ls())

require("ggmap")||install.packages("ggmap")
require("gsubfn")||install.packages("gsubfn")

library("ggmap")

##Extracting chat data 

chat_detail = readLines("G:\\chat.txt")

#Finding line# which contains Location Data

location = grep("location:",chat_detail)
# creating a blank Dataframe
df = data.frame(NULL)

# Looping throuugh the all lines of the file

for  (l in location){
  txt = chat_detail[l]
  split = strsplit(txt,"https://maps.google.com/\\?q=")  # Notice \\? in the pattern
  dateloc = split[[1]][1]
  loc = split[[1]][2]
  lat = strsplit(loc,",")[[1]][1]
  long = strsplit(loc,",")[[1]][2]
  name = gsub(": location: |^\\s+","",strsplit(dateloc,' ')[[1]][3])
  # gsub("-|:|^\\s+","",strapplyc(dateloc,"-.*?:"))     # from gsubfn
  date = strsplit(strsplit(dateloc,'-')[[1]][1],",")[[1]][1]
  description = strsplit(chat_detail[l+1],": ")[[1]][3]
  dft = data.frame(name,date,lat,long,description, stringsAsFactors = F)
  df = rbind(df,dft)
}

df$lat = as.numeric(df$lat)
df$long = as.numeric(df$long)

my_location = df[df$name == "Surendra",]

theme_set(theme_bw(8))
mylocationMap <- qmap(location = "Qutab Minar", zoom = 8, color = "bw", legend = "topleft")

mylocationMaps <- qmap(location = "Qutab Minar", zoom = 8,  scale = 5000, maptype = "toner-lite", legend = "topleft")

mylocationMaps <- qmap(location = "Qutab Minar", zoom = 8,  scale = 5000, maptype = "toner-lite", legend = "topleft")


```

## Including Plots

My Travel Interesting Stories:

With the whatsapp chat history, I saw an interesting stories about my travel that i didn't travel much (You can see the whats app data) so can certainly say "I am not a Travel person". I can see that my preferred way of commuting is public transport (Being in Delhi NCR, Metro is best public transport), so contributing to the environment.


```{r pressure, echo=FALSE}
mylocationMaps +  geom_point(aes(x = long, y = lat, colour = description), data = my_location)
```


